### 2021-08-16 sections/healthcare_application/main.tex
Fix figure labels and include some citations

In order to analyse the strategies played by the two EDs, the learning algorithm
asymmetric replicator dynamics is used.
% TODO: Cite asymmetric replicator dynamics
The use of a learning algorithm allows to investigate, not only the outcome of 
the game, but also how that outcome is reached.
Consider figure \ref{fig:ard-by-itself}. 
By running asymmetric replicator dynamics on the system the behaviour that 
emerges can be observed.
It can be seen that for these particular set of parameters 
(\ref{eq:ard-parameters}), the strategies of the two hospitals converge over 
time. 
Both hospital 1 (row player) and hospital 2 (column player) seem to be playing 
the same strategy \(s_10\) which indicates that thresholds \(T_1 = 10\) and 
\(T_2 = 10\) are played.
What is more important in this example is how the two hospitals reached these
decisions which also highlights the importance of using a learning algorithm.
Hospital 2 is able to reach the decision in a very short time while hospital 1
takes longer to get there.

\begin{figure}[H]
    \centering
    \includegraphics[scale=0.4, trim=120 0 120 0]{imgs/asymmetric_rd/asymmetric_rd.png}
    \label{fig:ard-by-itself}
    \caption{Asymmetric replicator dynamics run}
\end{figure}

\begin{multicols}{3}
    \begin{itemize} \label{eq:ard-parameters}
        \item \( \lambda_{1_1} \) = 1
        \item \( \mu_1 \) = 2
        \item \( C_1 \) = 2
        \item \( N_1 \) = 10
        \item \( M_1 \) = 6

@@

To study such effects a new concept is introduced that considers the ratio 
between each hospital's best achievable blocking time and the one that is being
played.
This new concept is defined as the compartmentalised price of anarchy of the 
players of the game and is defined as \(PoA_i(\tilde{s})\), where 
\(i \in [1, 2]\) to distinguish among the two players/hospitals where 
\(\tilde{s}\) is the strategy that is being played by player \( i \). 
The compartmentalised price of anarchy aims to measure inefficiencies in the 
model.
The \(PoA\) for the blocking time of player \(i\) for strategy \(\tilde{s}\) 
is given by:

@@

Using equation (\ref{eq:poa_compartmentalised}) and asymmetric replicator 
dynamics the game can be simulated and show the compartmentalised price of 
anarchy at every iteration for both players.
Figure \ref{fig:ard_original} shows the strategies that are being played and 
the values of \(PoA_1(s)\) and \(PoA_2(s)\) for all iterations of the 
learning algorithm until it reaches an evolutionary stable pair of strategies.

\begin{figure}[H]
    \includegraphics[width=\textwidth, trim=0 400 0 0]{imgs/asymmetric_rd_and_PoA/asymmetric_original.pdf}
    \caption{The strategies played when running asymmetric replicator dynamics
    along with the compartmentalised price of anarchy of the blocking time at
    each iteration of the learning algorithm}
    \label{fig:ard_original}
\end{figure}

@@

Figure \ref{fig:ard_lambda_2} shows a similar run of the
algorithm but when the strategies begin to stabilise a huge increase in the
arrival rate of ambulances occurs (i.e \( \lambda_2 = 10.7 \)).

\begin{figure}[H]
    \includegraphics[width=\textwidth, trim=0 400 0 0]{imgs/asymmetric_rd_and_PoA/asymmetric_flooding.pdf}
    \caption{The strategies played when running asymmetric replicator dynamics
    along with the compartmentalised price of anarchy of the blocking time at
    each iteration of the learning algorithm. After a number of iterations the 
    arrival rate of ambulance patients is significantly increased to flood the
    system completely \( \lambda_2 = 10.7 \).}
    \label{fig:ard_lambda_2}
\end{figure}

By increasing \(\lambda_2\) there is no change in the how the players behave
(\(T_1 = 5, T_2 = 6\)), but the outcome of the system does change. 
There is a decline in the price of anarchy of the blocking time which at first 
glance indicates that upon flooding the system it becomes more efficient. 
This is non-sensical though.
What it really shows is that the steep increase in \( \lambda_2 \) simply leaves 
less potential for improvement.

Figure \ref{fig:ard_num_of_servers} shows a run of asymmetric replicator 
dynamics with a change in the number of servers of both models.
The number of servers are increased from \(C_1 = 3, C_2 = 2\) to 
\(C_1 = 4, C_2 = 3\).

\begin{figure}[H]
    \includegraphics[width=\textwidth, trim=0 400 0 0]{imgs/asymmetric_rd_and_PoA/asymmetric_increase_C.pdf}
    \caption{
        The strategies played when running asymmetric replicator dynamics
        along with the compartmentalised price of anarchy of the blocking time 
        at each iteration of the learning algorithm. After a number of 
        iterations the number of servers for both systems are increased by one.
    }
    \label{fig:ard_num_of_servers}
\end{figure}

In this case the both the behaviour as well as the price of anarchy change.
The players change their strategies from \(T_1 = 5, T_2 = 6\) to 
\(T_1 = 6, T_2 = 7\) and the \(PoA\) of the blocking time goes down.
By adding more resources to the models they are able to increase their 
efficiency.
Although this is a good way to escape such inefficiencies, it might not always
be cost efficient.

Figure \ref{fig:ard_penalty} is slightly different than the previous ones.
Once asymmetric replicator dynamics becomes stable on some inefficient 
strategies (in terms of the blocking time) the payoff matrices of the two are
scaled in such a way so that the selected strategy is penalised.

\begin{figure}[H]
    \includegraphics[width=\textwidth, trim=0 400 0 0]{imgs/asymmetric_rd_and_PoA/asymmetric_penalty.pdf}
    \caption{
        The strategies played when running asymmetric replicator dynamics
        along with the compartmentalised price of anarchy of the blocking time 
        at each iteration of the learning algorithm. After a number of 
        iterations the most dominant strategy is being penalised.
    }
    \label{fig:ard_penalty}
\end{figure}

By incentivising the players in such a way the players change their strategies 
and ambulance patients are accepted in the ED more often.
Thus the blocking time \(PoA\) for both EDs drops down.

>>>>

In order to analyse the strategies played by the two EDs, the learning algorithm
asymmetric replicator dynamics is used \cite{asymmetricreplicatordynamics}.
The use of a learning algorithm allows to investigate, not only the outcome of 
the game, but also how that outcome is reached.
Consider figure \ref{fig:ard-by-itself}. 
By running asymmetric replicator dynamics on the system the behaviour that 
emerges can be observed.
It can be seen that for these particular set of parameters the strategies of 
the two hospitals converge over time. 
Both hospital 1 (row player) and hospital 2 (column player) seem to be playing 
the same strategy \(s_10\) which indicates that thresholds \(T_1 = 10\) and 
\(T_2 = 10\) are played.
What is more important in this example is how the two hospitals reached these
decisions which also highlights the importance of using a learning algorithm.
Hospital 2 is able to reach the decision in a very short amount of time while 
hospital 1 takes longer and goes through numerous strategies to get there.

\begin{figure}[H]
    \centering
    \includegraphics[scale=0.4, trim=120 0 120 0]{imgs/asymmetric_rd/asymmetric_rd.png}
    \caption{Asymmetric replicator dynamics run}
    \label{fig:ard-by-itself}
\end{figure}

\begin{multicols}{3}
    \begin{itemize}
        \item \( \lambda_{1_1} \) = 1
        \item \( \mu_1 \) = 2
        \item \( C_1 \) = 2
        \item \( N_1 \) = 10
        \item \( M_1 \) = 6

@@

To study the efficiency of the strategies being played a new concept is 
introduced that considers the ratio between each hospital's best achievable 
blocking time and the one that is being played.
This new concept is defined as the compartmentalised price of anarchy of the 
players of the game and is defined as \(PoA_i(\tilde{s})\), where 
\(i \in [1, 2]\) to distinguish among the two players/hospitals where 
\(\tilde{s}\) is the strategy that is being played by player \( i \). 
The compartmentalised price of anarchy aims to measure inefficiencies in the 
model.
The \(PoA\) for the blocking time of player \(i\) for strategy \(\tilde{s}\) 
is given by:

@@

\textbf{Base run:}
Using equation (\ref{eq:poa_compartmentalised}) and asymmetric replicator 
dynamics the game can be simulated and show the compartmentalised price of 
anarchy at every iteration for both players.
Figure \ref{fig:ard_original} shows the strategies that are being played and 
the values of \(PoA_1(s)\) and \(PoA_2(s)\) for all iterations of the 
learning algorithm until it reaches an evolutionary stable pair of strategies.

\begin{figure}[H]
    \includegraphics[width=\textwidth]{imgs/asymmetric_rd_and_PoA/asymmetric_original.pdf}
    \caption{The strategies played when running asymmetric replicator dynamics
    along with the compartmentalised price of anarchy of the blocking time at
    each iteration of the learning algorithm}
    \label{fig:ard_original}
\end{figure}

@@

\textbf{Increasing \(\lambda_2\):}
Figure \ref{fig:ard_lambda_2} shows a similar run of the
algorithm but when the strategies begin to stabilise a huge increase in the
arrival rate of ambulances occurs (i.e \( \lambda_2 = 10.7 \)).

\begin{figure}[H]
    \includegraphics[width=\textwidth]{imgs/asymmetric_rd_and_PoA/asymmetric_flooding.pdf}
    \caption{The strategies played when running asymmetric replicator dynamics
    along with the compartmentalised price of anarchy of the blocking time at
    each iteration of the learning algorithm. After a number of iterations the 
    arrival rate of ambulance patients is significantly increased to flood the
    system completely \( \lambda_2 = 10.7 \).}
    \label{fig:ard_lambda_2}
\end{figure}

By increasing \(\lambda_2\) there is no change as to how players behave
(\(T_1 = 5, T_2 = 6\)), but the efficiency of the system does change. 
There is a decline in the price of anarchy of the blocking time which at first 
glance indicates that upon flooding the system it becomes more efficient. 
This is non-sensical though.
What it really shows is that the steep increase in \( \lambda_2 \) simply leaves 
less potential for improvement.

\textbf{Increasing number of servers \( C_1 and C_2 \):}
Figure \ref{fig:ard_num_of_servers} shows a run of asymmetric replicator 
dynamics with a change in the number of servers of the hospitals.
The number of servers are increased from \(C_1 = 3, C_2 = 2\) to 
\(C_1 = 4, C_2 = 3\).

\begin{figure}[H]
    \includegraphics[width=\textwidth]{imgs/asymmetric_rd_and_PoA/asymmetric_increase_C.pdf}
    \caption{
        The strategies played when running asymmetric replicator dynamics
        along with the compartmentalised price of anarchy of the blocking time 
        at each iteration of the learning algorithm. After a number of 
        iterations the number of servers for both systems are increased by one.
    }
    \label{fig:ard_num_of_servers}
\end{figure}

In this case, both the behaviour as well as the price of anarchy change.
The players change their strategies from \(T_1 = 5, T_2 = 6\) to 
\(T_1 = 6, T_2 = 7\) and the \(PoA\) of the blocking time goes down.
By adding more resources to the models they are able to increase their 
efficiency.
Although this is a good way to escape such inefficiencies, it might not always
be cost efficient.

\textbf{Incentivising players:}
From figures \ref{fig:ard_lambda_2} and \ref{fig:ard_num_of_servers} it can be
seen that we can change some parameters of the model to make it more efficient.
The approach used on figure \ref{fig:ard_penalty} is slightly different than 
the previous cases.
Once the played strategies in asymmetric replicator dynamics strategies 
converge the payoff matrices of the two are scaled in such a way so that the 
utilities of the selected strategy is penalised.

\begin{figure}[H]
    \includegraphics[width=\textwidth]{imgs/asymmetric_rd_and_PoA/asymmetric_penalty.pdf}
    \caption{
        The strategies played when running asymmetric replicator dynamics
        along with the compartmentalised price of anarchy of the blocking time 
        at each iteration of the learning algorithm. After a number of 
        iterations the most dominant strategy is being penalised.
    }
    \label{fig:ard_penalty}
\end{figure}

Figure \ref{fig:ard_penalty} shows that players start playing strategies 
\( T_1 = 5\) and \( T_2 = 6 \) and mid-run of the learning algorithm a penalty
is applied to these strategies on the payoff matrix.
By incentivising the players in such a way the players change their strategies 
to \(T_1 = 6\) and \(T_2 = 7\), and thus ambulance patients are accepted in the 
ED more often.
Hence, the \(PoA\) for both EDs is decreased, meaning that the whole system is
more efficient in terms of the blocking time.
